---
title: "Basics of data visualization"
author: "Julia Romanowska"
institute: "BIOS, UiB"
date: "20.05.2021"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
style_solarized_light(
  code_font_size = "0.7rem",
  code_inline_font_size = "0.9rem"
)

library(xaringanExtra)
use_clipboard()
use_scribble()
use_tachyons()
# use_webcam()
use_fit_screen()
use_panelset()

knitr::opts_chunk$set(
  fig.width = 6,
  message = FALSE,
  warning = FALSE,
  comment = "",
  cache = F,
  echo = FALSE
)
library(flipbookr)
library(tidyverse)
library(palmerpenguins)

library(countdown)
```

class: middle, center

## Julia Romanowska

### bioinformatics/biostatistics, visualization

### co-founder of R-Ladies Bergen

https://jrom.bitbucket.io/homepage/

---

class: inverse, bottom

## What this will *not* be:

- not a ggplot/R/programming course
- not an art course
- not much about color theory
- not much about tidying data

---

class: inverse, right, bottom

## What this will be:

- how to show your data to various audience
- how to choose the story in your data
- how to __start__ with ggplot2
- where to search for help

---

class: center

# Warmup

```{r}
countdown(minutes = 5, seconds = 0)
```

## TASK

> Grab a piece of paper and a pencil and draw this data!

```{r}
knitr::kable(
tibble::tribble(
~DATE, ~CAPACITY, ~DEMAND,
"2019-04", 29263, 46193,
"2019-05", 28037, 49131,
"2019-06", 21596, 50124,
"2019-07", 25895, 48850,
"2019-08", 25813, 47602,
"2019-09", 22427, 43697,
"2019-10", 23605, 41058,
"2019-11", 24263, 37364,
"2019-12", 24243, 34364
)
)
```

???

# Questions

- was it easy to imagine the data?
- how did you start drawing?
- did you change your point of view of the data _after_ you've sketched it?
- what questions arised when you saw the data plotted?


